intro

### 2022-01-28 06_Paper/ER-ED/TheoreticalBackground.Rmd
added packages for intro part

---
title: "intro"
author: "Christoph Scheffel"
output: html_document
---

# 1. Introduction

@@

## 1.1 ER strategies discounting

>>>>

---
title: "intro"
author: "Christoph Scheffel"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(targets)    # to keep track of all relevant files
library(here)       # to set directories without defined paths
library(papaja)     # APA conform output

# set top level directory to source file
here::i_am("flag_project_root_CERED.txt")
```
# 1. Introduction

@@

## 1.1 ER strategy discounting
